hormones

### 2020-02-03 analysis/07_hormones.Rmd
better table order

hormones$hormone <- factor(hormones$hormone, 
                           levels = c("prolactin", "corticosterone", "progesterone", 
                                      "estradiol", "testosterone"))
head(hormones)
```

@@

p1 <- hormones %>%
  filter(hormone == "corticosterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "CORT (ng/mL)", subtitle = element_blank() , x = NULL) +
  theme(legend.position = "none") +
  scale_fill_manual(values = sexcolors)
p1

@@

p2 <-  ggplot(cort, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = element_blank() ) +
  theme(legend.position = "none")

@@

PRLf <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization",
         sex == "female")

PRLm <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization",
         sex == "male")

p2a <-  ggplot(PRLf, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "females") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100))

p2b <-  ggplot(PRLm, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "males") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100))

@@

>>>>

hormones$hormone <- factor(hormones$hormone, 
                           levels = c("prolactin", "corticosterone", "progesterone", 
                                      "estradiol", "testosterone"))
hormones$logconc <- log10(hormones$plasma_conc)
head(hormones)
```

@@

p1 <- hormones %>%
  filter(hormone == "corticosterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "CORT (ng/mL)", subtitle = element_blank() , x = NULL) +
  theme(legend.position = "none") +
  scale_fill_manual(values = sexcolors) +
  scale_fill_manual(values = colorscharmaip)
p1

@@

p2 <-  ggplot(cort, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = element_blank() ) +
  theme(legend.position = "none")  +
  scale_fill_manual(values = colorscharmaip)

@@

PRLf <- hormones %>%
  filter(hormone == "prolactin",
         #study == "characterization",
         sex == "female")

PRLm <- hormones %>%
  filter(hormone == "prolactin",
         #study == "characterization",
         sex == "male")

p2a <-  ggplot(PRLf, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "females") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100))  +
  scale_fill_manual(values = colorscharmaip)

p2b <-  ggplot(PRLm, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "males") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100))+
  scale_fill_manual(values = colorscharmaip)

@@

## stats

```{r}

P3 <- hormones %>% filter(hormone == "progesterone")
E2 <- hormones %>% filter(hormone == "estradiol")
T2 <- hormones %>% filter(hormone == "testosterone")

aov1 <- aov(PRLm$logconc ~ PRLm$treatment)
res1 <- TukeyHSD(aov1)
res1 <- as.data.frame(res1$`PRLm$treatment`)
res1$hormone <- "male PRL"
res1$sig <- ifelse(res1$`p adj` < 0.001, "***",
                   ifelse(res1$`p adj` < 0.01, "**",
                           ifelse(res1$`p adj` < 0.05, "*", "NS" )))
res1$comparison <- row.names(res1)
res1

aov2 <- aov(PRLf$logconc ~ PRLf$treatment)
res2 <- TukeyHSD(aov2)
res2 <- as.data.frame(res2$`PRLf$treatment`)
res2$hormone <- "female PRL"
res2$sig <- ifelse(res2$`p adj` < 0.001, "***",
                   ifelse(res2$`p adj` < 0.01, "**",
                           ifelse(res2$`p adj` < 0.05, "*","NS"  )))
res2$comparison <- row.names(res2)
res2

aov3 <- aov(P3$logconc ~ P3$treatment)
res3 <- TukeyHSD(aov3)
res3 <- as.data.frame(res3$`P3$treatment`)
res3$hormone <- "P3"
res3$sig <- ifelse(res3$`p adj` < 0.001, "***",
                   ifelse(res3$`p adj` < 0.01, "**",
                           ifelse(res3$`p adj` < 0.05, "*", "NS"  )))
res3$comparison <- row.names(res3)
res3

aov4 <- aov(E2$logconc ~ E2$treatment)
res4 <- TukeyHSD(aov4)
res4 <- as.data.frame(res4$`E2$treatment`)
res4$hormone <- "E2"
res4$sig <- ifelse(res4$`p adj` < 0.001, "***",
                   ifelse(res4$`p adj` < 0.01, "**",
                           ifelse(res4$`p adj` < 0.05, "*", "NS" )))
res4$comparison <- row.names(res4)
res4

aov5 <- aov(T2$logconc ~ T2$treatment)
res5 <- TukeyHSD(aov5)
res5 <- as.data.frame(res5$`T2$treatment`)
res5$hormone <- "T"
res5$sig <- ifelse(res5$`p adj` < 0.001, "***",
                   ifelse(res5$`p adj` < 0.01, "**",
                           ifelse(res5$`p adj` < 0.05, "*", "NS"  )))
res5$comparison <- row.names(res5)
res5

resall <- rbind(res3, res5, res4, res2, res1) %>% drop_na()
resall

table1 <- resall %>%
  filter(grepl('control', comparison),
         !grepl('prolong|extend|m.', comparison)) %>%
   mutate(diff = round(diff, 2)) %>% 
  mutate(diffsig = paste(diff, sig, sep = ", ")) %>% 
   select(hormone, comparison, diffsig) %>% 
  pivot_wider( names_from = hormone, values_from = diffsig)
table1

table2 <- resall %>%
  filter(!grepl('control|bldg|lay|n5', comparison),
         grepl('prolong|extend|m.', comparison)) %>%
   mutate(diff = round(diff, 2)) %>% 
  mutate(diffsig = paste(diff, sig, sep = ", ")) %>% 
   select(hormone, comparison, diffsig) %>% 
  pivot_wider( names_from = hormone, values_from = diffsig)
table2

write.csv(table1, "../../parentalhormones/data/table-1.csv")
write.csv(table2, "../../parentalhormones/data/table-2.csv")
